\sc Cells at War: The Playfulness of Game-Based Learning

### 2023-03-15 thesis_template/paper0904.tex
Results writingcoming together

\lhead{Cells at War: Game-Based Learning} %This needs to change
\rhead{Bianca Flaim, Alexander Turco}
\title{\sc Cells at War: The Playfulness of Game-Based Learning}
\author{\sc Alexander Turco and Rosa da Silva}

@@

150 students enrolled in the winter 2021 session of BIO1A03 attended a game-based style lecture and completed the follow-up survey. Participants were asked a series of questions regarding their current experiences as undergraduate science students, as well as questions regarding the benefits of implementing game-based learning approaches into their classrooms.

@@

>>>>

\lhead{Cells at War: Game-Based Learning} %This needs to change
\rhead{Alexander Turco and Rosa da Silva}
\title{\sc Cells at War: The Playfulness of Game-Based Learning}
\author{\sc Alexander Turco and Rosa da Silva}

@@

150 students enrolled in the winter 2021 session of BIO1A03 attended a game-based style lecture and completed the follow-up survey. Students were presented with condensed lecture material prior to completing the relevant level in the game. The idea behind this was to provide a brief introduction of the content to students, and then allow them to further explore these concepts by playing the game.

Participants were asked a series of questions regarding their current experiences as undergraduate science students, as well as questions regarding the benefits of implementing game-based learning approaches into their classrooms. To gain insight into how experience students had playing video games, they were asked to indicate a weekly average amount of time spent playing them \figref{fig:1}. 66 Participants (44\%) indicated that they did not play video games, while 53 participants (36\%) indicated that they spent between 1-10 hours per week. Only 7 students (5\%) were found spending approximately 10-20 hours per week playing video games. It is interesting to note that participants who reported not playing video games also emphasized that the game was `easy to navigate' and `very accessible'. This suggests that a lack of experience playing video games did not necessarily limit students' abilities to learn course content through playing the game.

@@

Further data obtained provided insight into the various types of courses students were taking at McMaster University during the fall/winter 2021 semesters \figref{fig:2}. At this time, McMaster University was slowly shifting back to in-person classes due to COVID-19 restrictions being lifted, however, a large majority of courses had been converted to hybrid, blended learning, and online courses. 60 participants (40\%) indicated that the majority of courses they were taking were mostly hybrid or blended learning style courses. 28 participants (19\%) indicated most of their courses were back in-person, while only 7 participants (5\%) were enrolled in mostly online courses. 30 participants indicated a balanced mix of all course types. These results highlight the shift from traditional teaching practices towards newer, more innovative educational practices.
